---
title: "Using sunsynkr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using sunsynkr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`sunsynkr` helps you to acquire information about Sunsynk photovoltaic systems from their API. If you have a Sunsynk inverter and an account to view and manage it on [SunsynkConnect](https://sunsynk.net/), you should be able to use this package to retrieve information about your plant. 

Note that this package is unofficial and is in no way associated with Sunsynk. It may stop working (or return misleading outputs) at any time and without warning.

## Setup

First, load the package.

```{r setup}
library(sunsynkr)
```

### Authentication

You must configure environment variables to hold your sunsynk username and password (the ones you use to login to SunsynkConnect at https://sunsynk.net/). Configure the following environment variables:

- `SUNSYNK_USER`
- `SUNSYNK_PASS`

## Get a token

All `sunsynkr` functions which call the API require a token as an argument. Accordingly, you must first acquire an authentication token.

```{r}
token <- get_token()
token
```
You can now use this token to authenticate other `susynkr` functions to the API.

## Get plants details

```{r include=FALSE}
# Redact personal info
redact_character <- function(x) {
  gsub("\\w", "X", x)
}

redact_plants <- function(x) {
  
  plant_infos <- x$data$infos
  
  redact_plant <- function(x) {
    x$id <- redact_character(x$id)
    x$name <- redact_character(x$name)
    x$thumbUrl <- redact_character(x$thumbUrl)
    x$address <- redact_character(x$address)
    x$email <- redact_character(x$email)
    x$phone <- redact_character(x$phone)
    x$masterId <- redact_character(x$masterId)
    
    x
  }
  
  x$data$infos <- lapply(plant_infos, redact_plant)
  
  x
  
}


```

You can now get details of all plants associated with your account.

```{r}
plants <- get_plants(token)
```

```{r include=FALSE}
plant_id <- plants$data$infos[[1]]$id

plants <- plants |> 
  redact_plants()

```

The `sunsynkr_plants` object returned by `get_plants()` is also a list. For example, we can return the total kWh generated today for the first plant in the list with the following.

```{r}
plants[["data"]][["infos"]][[1]][["etoday"]]

```
Printing the `sunsynkr_plants` object returns a tibble summarising the information available for each plant.

```{r}
plants

```
Note that, currently, this function will return details of a maximum of 100 plants. 

## Flow

We can query the most recent power flow from the API for a given plant. We can extract the plant from `plants` like this. 

```{r eval=FALSE}
plant_id <- plants$data$infos[[1]]$id

```

Then, we can obtain the power flow for the plant.

```{r}
flow <- get_flow(token, 
                 plant_id)

```
The `sunsynkr_flow` object returned by `get_flow()` is also a list and you can access its elements in the conventional way. For example, to return the current state of charge of the battery...

```{r}
flow[["data"]][["soc"]]

```

Printing the `sunsynkr_flow` object outputs a representation of the power flows managed by the inverter.

```{r}
flow

```

## Day summary

You can return a summary of all power flows (and battery state of charge) at five minute intervals for a given day.

```{r}
date <- lubridate::today() - lubridate::days(1)


day_summary <- get_day_summary(token, 
                               plant_id, 
                               date)

```

`get_day_summary()` returns an object of `sunsynkr_day_summary` which is also a list. It's likely that you might want this information in a more convenient table form.

```{r}
day_summary_table <- get_day_summary_table(token, 
                                           plant_id, 
                                           date)

day_summary_table
```

You can also generate a plot of the day summary table.

```{r fig.height=6, fig.width=6}
plot(day_summary_table)
```

